Scaling rates of true polar wander in convecting planets and moons

### 2017-05-01 reply.tex
Reword statement in response.
Edits to reply.

\item Paragraphs added to introductory clauses.

@@

\item Line 396 is reworded, as suggested.

@@

\item How representative is Fig. 4? The answer is ``very''. There was no need to be selective about the examples we showed. The events in question are always present when convection is sufficiently vigorous. We completely agree that the rate of TPW is small when theta = 90. This fact is acknowledged in the revised manuscript and supported by pointed to this expectation in our equation for the rate of TPW. However, embedding this equation in a mantle convection simulation reveals some interesting complications because the mass anomalies that cause TPW are always in motion.

>>>>

\item We add commas to or invert the relevant sentences.

@@

\item Line 396 does not assume $\theta$ to be small. We have elaborated on the cited literature to clarify this point.

@@

\item How representative is Fig. 4? The answer is ``very''. There was no need to be selective about the examples we showed. The events in question are always present when convection is sufficiently vigorous. We completely agree that the rate of TPW is small when theta = 90. This fact is acknowledged in the revised manuscript and confirmed in our equation for the rate of TPW. However, embedding this equation in a mantle convection simulation reveals some interesting complications because the mass anomalies that cause TPW are always in motion.

### 2017-05-01 tpw_rate.tex
Edits to reply.

 Much of the debate about the magnitude of TPW on Earth comes down to the question of how big $\theta$ can be \citep{kirschvink1997evidence, steinberger1997changes}. In the next section we seek to characterize the maximum value for $\theta$ in terms of the dimensionless parameters.

>>>>

 Much of the debate about the magnitude of TPW on Earth comes down to the question of how big $\theta$ can be. \citet{kirschvink1997evidence} hypothesized about an event where $\theta$ was approximately 90$^\circ$, while many geodynamic simulations of recent TPW assume that $\theta$ is small \citep{steinberger1997changes}. In the next section we seek to characterize the maximum value for $\theta$ in terms of the dimensionless parameters.
